\textbf{Minimum Array Partition}

### 2023-09-28 paper/paper.tex
Paper - add BF and GA descriptions and begin evaluation
Paper basic layout

\begin{verbatim}
Testcase: tests/linear_n20_p4.in
  BRUTE FORCE
    Results  : BEST=602        WORST=602        AVG=602.00    
    Time (s) : BEST=4.71       WORST=5.17       AVG=4.99      
  GENETIC ALGORITHM (GA) [pop_size=20, num_iters=100, elitism_size=4]
    Results  : BEST=602        WORST=602        AVG=602.00    
    Time (s) : BEST=0.17       WORST=0.18       AVG=0.17      
  SIMULATED ANNEALING (SA)
    Results  : BEST=602        WORST=602        AVG=602.00    
    Time (s) : BEST=0.32       WORST=0.34       AVG=0.33      
  VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=400]
    Results  : BEST=602        WORST=608        AVG=603.20    
    Time (s) : BEST=0.18       WORST=0.20       AVG=0.19

Testcase: tests/linear_n30_p4.in
  BRUTE FORCE - skipping due to speed
  GENETIC ALGORITHM (GA) [pop_size=30, num_iters=150, elitism_size=6]
    Results  : BEST=1920       WORST=1968       AVG=1958.40   
    Time (s) : BEST=0.37       WORST=0.39       AVG=0.38      
  SIMULATED ANNEALING (SA)
    Results  : BEST=1920       WORST=1920       AVG=1920.00   
    Time (s) : BEST=0.32       WORST=0.35       AVG=0.34      
  VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=900]
    Results  : BEST=1920       WORST=1968       AVG=1939.20   
    Time (s) : BEST=0.43       WORST=0.44       AVG=0.43 
\end{verbatim}

We find the results for $squared$ test the most intersting.

\begin{verbatim}
Testcase: tests/squared_n40_p3.in
  BRUTE FORCE
    Results  : BEST=214662     WORST=214662     AVG=214662.00 
    Time (s) : BEST=1.60       WORST=1.72       AVG=1.65      
  GENETIC ALGORITHM (GA) [pop_size=40, num_iters=200, elitism_size=8]
    Results  : BEST=214662     WORST=215757     AVG=215538.00 
    Time (s) : BEST=0.52       WORST=0.53       AVG=0.52      
  SIMULATED ANNEALING (SA)
    Results  : BEST=214662     WORST=214662     AVG=214662.00 
    Time (s) : BEST=0.13       WORST=0.13       AVG=0.13      
  VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=1600]
    Results  : BEST=214662     WORST=215757     AVG=215538.00 
    Time (s) : BEST=0.30       WORST=0.31       AVG=0.30

Testcase: tests/squared_n40_p4.in
  BRUTE FORCE - skipping due to speed
  GENETIC ALGORITHM (GA) [pop_size=40, num_iters=200, elitism_size=8]
      Results  : BEST=124440     WORST=131775     AVG=125907.00 
      Time (s) : BEST=0.66       WORST=0.69       AVG=0.68      
  SIMULATED ANNEALING (SA)
      Results  : BEST=124440     WORST=124440     AVG=124440.00 
      Time (s) : BEST=0.31       WORST=0.33       AVG=0.32      
  VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=1600]
      Results  : BEST=124440     WORST=131775     AVG=125907.00 
      Time (s) : BEST=0.76       WORST=0.81       AVG=0.78

Testcase: tests/squared_n100_p10.in
  BRUTE FORCE - skipping due to speed
  GENETIC ALGORITHM (GA) [pop_size=100, num_iters=500, elitism_size=20]
    Results  : BEST=858130     WORST=984543     AVG=941758.40 
    Time (s) : BEST=14.10      WORST=14.69      AVG=14.47     
  SIMULATED ANNEALING (SA)
    Results  : BEST=903805     WORST=1149356    AVG=1030165.60
    Time (s) : BEST=4.56       WORST=4.85       AVG=4.69      
  VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=10000]
    Results  : BEST=837551     WORST=928305     AVG=868049.20 
    Time (s) : BEST=28.35      WORST=33.75      AVG=30.67 
\end{verbatim}

>>>>

\begin{verbatim}
Testcase: tests/linear_n20_p4.in
BRUTE FORCE
        Results  : BEST=602        WORST=602        AVG=602.00    
        Time (s) : BEST=4.71       WORST=5.17       AVG=4.99      
    GENETIC ALGORITHM (GA) [pop_size=20, num_iters=100, elitism_size=4]
        Results  : BEST=602        WORST=602        AVG=602.00    
        Time (s) : BEST=0.17       WORST=0.18       AVG=0.17      
    SIMULATED ANNEALING (SA)
        Results  : BEST=602        WORST=602        AVG=602.00    
        Time (s) : BEST=0.32       WORST=0.34       AVG=0.33      
    VARIABLE NEIGHBOURHOOD SEARCH (VNS) [num_iters=400]
        Results  : BEST=602        WORST=608        AVG=603.20    
        Time (s) : BEST=0.18       WORST=0.20       AVG=0.19    
\end{verbatim}
